### 2019-03-11 reports/thesis/chapters/5_inference.tex
Start on inference chapter

The aim of this project was to obtain an x-ray image of a 3D printed sample and compare it with a simulation of that scan using software called \texttt{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \texttt{aRTist} can simulate x-ray scans of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the blueprint of the 3D printed sample \citep{bellon2011simulation, deresch2012simulating}. Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods, however this is outside the scope of this thesis.

@@

A pixel by pixel inference was proposed to do defect detection. A statistic $z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This statistic is
\begin{equation}
    Z_{x,y} = 
    \dfrac{
        \text{scan}_{x,y} - \text{aRTist}_{x,y}
    }
    {
        \sqrt{\widehat{\variance}\left[\text{scan}_{x,y}\right]}
    }
\end{equation}
where $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the scan. Under mild assumptions, it was shown in the previous chapters that the grey values in the scan were Normal. Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the $z_{i,j}$ statistics can be quantified
\begin{equation}
Z_{i,j}\sim \normal(0,1) \ .
\end{equation}
As with usual statistical convention, upper case $Z$ denote a random variable. Whereas lower case $z$ denote a realisation or an observation of that random variable.

The estimation of the grey value variance, that is $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ is be explained here. The variance model can be calibrated, or trained, by holding out a number replicated x-ray scans of a 3D printed sample. These replicated x-ray scans provide variance-mean data which was used to train the variance model, such as a Gamma distributed GLM. The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model. The variance was then predicted using the grey value in the \texttt{aRTist} simulation.

This method for inference was applied to the dataset \texttt{Sep16 120deg}. Here a cuboid with voids were purposefully manufactured to see if they can be detected. The 20 x-ray images were spilt into 2. 19 images were used to train the variance-mean model. One image, called the test image, was used to compare with \texttt{aRTist}, as shown in Figure \ref{fig:inference_initial_artist_scan_aRTist}. In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_scan.eps}
        \caption{X-ray image}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_aRTist.eps}
        \caption{\texttt{aRTist} simulation}
    \end{subfigure}
    }
    \caption{An x-ray scan of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset. This can be compared directly to the \texttt{aRTist} simulation for defects.}
    \label{fig:inference_initial_artist_scan_aRTist}
\end{figure}

For each pixel, a $z$ statistic was calculated. A $z$ statistic too large in magnitude can be considered to be evidence of a positive result. Another way to represent the $z$ statistic is the $p$-value which is given as
\begin{equation}
    p_{x,y} = 2(1-\Phi(\|z_{x,y}\|))
\end{equation}
which can takes values $0\leqslant p_{i,j} \leqslant 1$. A $p$-value too small is considered to be evidence of a defect. The resulting $z$ statistics and $p$-values are shown in Figure \ref{fig:inference_initial_artist_logp_z}.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_logp.eps}
        \caption{$-\log p\text{-values}$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_image.eps}
        \caption{$z$ statistics}
    \end{subfigure}
    }
    \caption{The resulting $z$ statistics and $p$ values comparing an x-ray scan with the \texttt{aRTist} simulation.}
    \label{fig:inference_initial_artist_logp_z}
\end{figure}

The resulting $z$ statistics and $p$-values are concerning. This is because the $p$-values are not very smooth on the surfaces of the sample. It should be expected that small $p$-values are in areas of the defects. Pixels are significant, or considered to be evidence of a defect, when for $\|z_{x,y}\|>\input{../tables/initial_artist_z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} (BH) procedure at the $z_\alpha = 2$ significance level. The significant pixels are shown in Figure \ref{fig:inference_initial_artist_sig_pixels}.

@@

Model misspecification appeared to be the main source of error. The $z$ statistics was inspected using a histogram and a QQ plot, as shown in Figure \ref{fig:inference_initial_artist_z_histo}. It can be seen that the $z$ statistics does not look Normal which seems to suggest that the assumption of $z_{i,j}\sim \normal(0,1)$ is incorrect. However this assumption can relaxed and can be done using the empirical null \citep{efron2004large}.

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/inference/initial_artist_sig_pixels.eps}
    \caption{Significant pixels highlighted using the BH procedure at the $z_\alpha = 2$ significance level.}
    \label{fig:inference_initial_artist_sig_pixels}
\end{figure}

\begin{figure}
    \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_histo.eps}
    	\caption{Histogram}
    \end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_qq.eps}
    	\caption{QQ plot}
    \end{subfigure}
	}
    \caption{Distribution of the  $z$ statistics with the BH procedure critical region at the $z_\alpha=2$ level.}
    \label{fig:inference_initial_artist_z_histo}
\end{figure}

This chapter covers hypothesis testing, for a single test and then for multiple tests, treating each pixel as a test. The empirical null is reviewed and then extended to an image filter, called the empirical null filter. This filter adjust each $z$ statistic according to its neighbours, ironing out false positive results. Simulations and actual results was shown at the end of the chapter.

@@

The Newton-Raphson method is an iterative algorithm and requires an initial value $z^{(0)}$. The iterative step is
\begin{equation}
	z^{(r+1)} =
	z^{(r)}
	-\dfrac{
		\left.
			\dfrac{
				\partial
			}
			{
				\partial z
			}
			\ln\widehat{p}_Z(z)
		\right|_{z = z^{(r)}}
	}
	{
		\left.
			\dfrac{
				\partial^2
			}
			{
				\partial z^2
			}
			\ln\widehat{p}_Z(z)
		\right|_{z = z^{(r)}}
	} 
\end{equation}
for $r=0,1,2,3,\dotdotdot$ until some convergence condition is met. The derivatives for the log density was obtained via the following. Recall that the kernel density estimate is
\begin{equation}
	\widehat{p}_Z(z)=
	\frac{1}{nh}
	\sum_{i=1}^n\phi\left(
		\dfrac{z_i-z}{h}
	\right)
	\tag{\ref{eq:inference_kernel_density_estimate}}
\end{equation}
so that the log density is
\begin{equation}
	\ln\widehat{p}_Z(z)=
	\ln\left(
		\dfrac{1}{nh}
	\right)
	+
	\ln\left[
		\sum_{i=1}^n
		\phi\left(
			\dfrac{
				z_i - z
			}
			{
				h
			}
		\right)
	\right]
	\ .
\end{equation}
Taking the first derivative
\begin{equation}
	\dfrac{
		\partial
	}
	{
		\partial z
	}
	\ln\widehat{p}_Z(z)
	=
	\dfrac{
		1
	}
	{
		\sum_{i=1}^n
		\phi\left(
			\dfrac{
				z_i - z
			}
			{
				h
			}
		\right)
	}
	\times
	\sum_{i=1}^n
	\phi'\left(
		\dfrac{
			z_i - z
		}
		{
			h
		}
	\right)
	\left(
		-\dfrac{
			1
		}
		{
			h
		}
	\right)
	\ .
\end{equation}
Using the fact that $\phi(z)=(2\pi)^{-1/2}\exp(-z^2/2)$, then $\phi'(z)=-z\phi(z)$. This is used to simplify the equation to be
\begin{equation}
	\dfrac{
		\partial
	}
	{
		\partial z
	}
	\ln\widehat{p}_Z(z)
	=
	\dfrac{
		\sum_{i=1}^n
		\phi\left(
			\dfrac{
				z_i - z
			}
			{
				h
			}
		\right)
		\left(
			\dfrac{
				z_i - z
			}
			{
				h
			}
		\right)
	}
	{
		h
		\sum_{i=1}^n
		\phi\left(
			\dfrac{
				z_i - z
			}
			{
				h
			}
		\right)
	}
	\ .
\end{equation}
Taking the derivative again
\begin{multline}
	\dfrac{
		\partial^2
	}
	{
		\partial z^2
	}
	\ln\widehat{p}_Z(z)
	=
	\left[
		h\sum_{i=1}^n
		\phi\left(
			\dfrac{
				z_i-z
			}
			{
				h
			}
		\right)
	\right]^{-2}
	\times
	\left\{
		h\left[
			\sum_{i=1}^n
			\phi\left(
				\dfrac{
					z_i-z
				}
				{
					h
				}
			\right)
		\right]
	\right.
	\\
	\left.
		\times
		\sum_{i=1}^n\left[
			\phi'\left(
				\dfrac{
					z_i-z
				}
				{
					h
				}
			\right)
			\left(
				-\dfrac{
					1
				}
				{
					h
				}
			\right)
			\left(
				\dfrac{
					z_i-z
				}
				{
					h
				}
			\right)
			+\phi\left(
				\dfrac{
					z_i-z
				}
				{
					h
				}
			\right)
			\left(
				-\dfrac{
					1
				}
				{
					h
				}
			\right)
		\right]
	\right.
	\\
	\left.
		-
		\left[
			\sum_{i=1}^n
			\phi\left(
				\dfrac{
					z_i-z
				}
				{
					h
				}
			\right)
			\left(
				\dfrac{
					z_i-z
				}
				{
					h
				}
			\right)
		\right]
		\left[
			h\sum_{i=1}^n
			\phi'\left(
				\dfrac{
					z_i-z
				}
				{
					h
				}
			\right)
			\left(
				-\dfrac{
					1
				}
				{
					h
				}
			\right)
		\right]
	\right\}
	\ .
\end{multline}
Using the fact that $\phi'(z)=-z\phi(z)$, then it is simplified to
\begin{multline}
	\dfrac{
		\partial^2
	}
	{
		\partial z^2
	}
	\ln\widehat{p}_Z(z)
	=
	\left[
		h\sum_{i=1}^n
		\phi\left(
			\dfrac{
				z_i-z
			}
			{
				h
			}
		\right)
	\right]^{-2}
	\times
	\left\{
		\left[
			\sum_{i=1}^n
			\phi\left(
				\dfrac{
					z_i-z
				}
				{
					h
				}
			\right)
		\right]
	\right.
	\\
	\left.
		\times
		\left[
			\sum_{i=1}^n
			\phi\left(
				\dfrac{
					z_i-z
				}
				{
					h
				}
			\right)
			\left(
				\left(
					\dfrac{
						z_i-z
					}
					{
						h
					}
				\right)^2
				-1
			\right)
		\right]
		-
		\left[
			\sum_{i=1}^n
			\phi\left(
				\dfrac{
					z_i-z
				}
				{
					h
				}
			\right)
		\right.
	\right.
	\\
	\left.
		\left.
			\left(
				\dfrac{
					z_i-z
				}
				{
					h
				}
			\right)
		\right]^2
	\right\}
	\ .
\end{multline}

@@

@@

The choice of the bandwidth $h$ is important for the kernel density estimator. It controls how smooth the kernel density estimator is, with higher values of $h$ producing smoother curves \citep{friedman2001elements}. Cross validation methods do exist \citep{bowman1984alternative, sheather2004density} but they can be computationally expensive. Rules of thumb \citep{silverman1986density, sheather2004density} can be used instead and are typically of the form
\begin{equation}
	h = bn^{-1/5}\times\text{min}\left(s_z,\text{IQR}_z/1.34\right)
\end{equation}
where $b=0.9$ \citep{silverman1986density}. This rule of thumb was developed with consideration of bimodal Normal distributions \citep{silverman1986density}. Other options include $b=1.06$ and $b=1.144$ to produce smoother curves \citep{sheather2004density}.

In the context of the empirical null, the kernel density estimator is only used to obtain values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$. Thus a good bandwidth is one which has good properties of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ rather than the density estimate. However exact properties of these estimators based on the kernel density estimators can be rather complicated. Empirical properties is studied here.

An experiment was conducted to investigate the behaviour of the estimators, $\widehat{\mu}_0$ and $\widehat{\sigma}_0$, on a dataset of $n$ simulated all null $\normal(0,1)$. Various values of $h$ and $n$ were investigated. In reality non-null test statistics may appear in the dataset but they should not be too common and interfere with the density estimate too much. For a given $h$ and $n$, 50 values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ were obtained by repeating the simulation. The median squared error, over the 50 repeats, for each of the estimators were plotted as shown in Figure \ref{fig:inference_ZNull1}.

@@

A smooth valley can be seen for the median squared error for $\widehat{\sigma}_0$. It appears for a given $n$, there exist a bandwidth which minimise the median squared error. However the rules of thumb does not optimise for $\widehat{\sigma}_0$ and undershoots it. This can be particularly seen in Figure \ref{fig:inference_ZNull2} where the median values of $\widehat{\sigma}_0$ are plotted. In this simulation, the true value is $\sigma_0=1$ and all rules of thumb produced biased estimates, in particular underestimates it.

\begin{figure}
	\centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error1.eps}
        \caption{$\mu_0$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error2.eps}
        \caption{$\sigma_0$}
    \end{subfigure}
    \caption{Median squared error of the estimators of the empirical null parameters from 50 repeats of $n$ simulated $\normal(0,1)$ data. Lines represent the rule of thumb for various values of $b$.}
    \label{fig:inference_ZNull1}
\end{figure}

\begin{figure}
	\centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error3.eps}
        \caption{Heatmap}
    \end{subfigure}
    \caption{Median value of $\widehat{\sigma}_0$ from 50 repeats of $n$ simulated $\normal(0,1)$ data. On the right, lines represent the rule of thumb for various values of $b$. On the left shows the true value of $\sigma_0=1$ as a plane, the empirical truth is where that plan intersects the surface.}
    \label{fig:inference_ZNull2}
\end{figure}

Overestimates and underestimates are both dangerous, but it depends on the importance of false positives and false negatives. This is because $\widehat{\sigma}_0$ was used to rescale the test statistics accordingly. Recall that the corrected test statistics are
\begin{equation}
	\zeta_i = \dfrac{
		z_i - \widehat{\mu}_0
	}
	{
		\widehat{\sigma}_0
	}
	\ .
	\tag{\ref{eq:inference_zeta}}
\end{equation}
Low values of $\widehat{\sigma}_0$ produce large values in magnitude of $\zeta_i$, potentially testing more of these test statistics as significant. High values of $\widehat{\sigma}_0$ does the opposite. Large number of positive results can led to more false positive results and vice versa.

The optimal bandwidth for a given $n$ was found numerically. Such a relationship can be seen in Figure \ref{fig:inference_ZNull_mse_plot} which plots the log squared error against the bandwidth for various $n$. A local quadratic regression \citep{friedman2001elements} was fitted and this was used to find the bandwidth which minimises the log squared error for a given $n$.

>>>>

The aim of this project was to obtain an x-ray image of a 3D printed sample and compare it with a simulation of that scan using software called \texttt{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \texttt{aRTist} can simulate x-ray acquisitions of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the computer aided design (CAD) of the 3D printed sample \citep{bellon2011simulation, deresch2012simulating}. Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods, however this is outside the scope of this thesis.

@@

A pixel by pixel inference was proposed to do defect detection. A statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This statistic is
\begin{equation}
    Z_{x,y} = 
    \dfrac{
        \text{scan}_{x,y} - \texttt{aRTist}_{x,y}
    }
    {
        \sqrt{\widehat{\variance}\left[\text{scan}_{x,y}\right]}
    }
\end{equation}
where $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the scan. Under mild assumptions, it was shown in the previous chapters that the grey values in the scan were Normal. Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the $Z_{i,j}$ statistics can be approximately quantified
\begin{equation}
Z_{x,y}\sim \normal(0,1) \ .
\end{equation}
As with usual statistical convention, upper case $Z$ denote a random variable. Whereas lower case $z$ denote a realisation or an observation of that random variable.

The variance model, $\widehat{\variance}\left[\text{scan}_{i,j}\right]$, can be calibrated, or trained, by holding out a number replicated x-ray images of a 3D printed sample. These replicated x-ray images were manually segmented. This provided variance-mean data and was used to train the variance model, such as a Gamma distributed GLM. The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model. The variance was then predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable.

This method for inference was applied to the dataset \texttt{Sep16 120deg}. Here a cuboid with voids were purposefully manufactured to see if they can be detected, the CAD shown in Figure \ref{fig:inference_testObject}. The 20 x-ray images were spilt into 2. 19 images were used to train the variance-mean model. One image, called the test image, was used to compare with \texttt{aRTist}. In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there. The test image and the \texttt{aRTist} simulation is shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist}.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
  \caption{CAD of a 3D cuboid with voids}
  \label{fig:inference_testObject}
\end{figure}

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_scan.eps}
      \caption{X-ray image}
      \label{fig:inference_inferenceIntro_inference_scan}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_artist.eps}
      \caption{\texttt{aRTist} simulation}
      \label{fig:inference_inferenceIntro_inference_artist}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_logp.eps}
      \caption{$-\log p\text{-values}$}
      \label{fig:inference_inferenceIntro_inference_pvalue}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_positivePixels.eps}
      \caption{Positive pixels}
      \label{fig:inference_inferenceIntro_inference_positivePixels}
    \end{subfigure}
  }
  \caption{An x-ray image of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset, was compared to the \texttt{aRTist} simulation to detect the purposefully manufactured voids. The $p$-values obtained were used for hypothesis testing using the \cite{benjamini1995controlling} procedure, controlling the FDR at the 5\% level. Pixels detected as positive are shown in red in d).}
  \label{fig:inference_inferenceIntro_inference}
\end{figure}

For each pixel, a $z$ statistic was calculated. A $z$ statistic too large in magnitude will classify that pixel as a positive result. In the hypothesis testing framework \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be used to represent $z$ statistic in a different way
\begin{equation}
    p_{x,y} = 2(1-\Phi(\|z_{x,y}\|))
\end{equation}
which can takes values $0\leqslant p_{x,y} \leqslant 1$. A $p$-value too small is considered a positive result. The $p$-values are shown in Figure \ref{fig:inference_inferenceIntro_inference_pvalue}.

The resulting $p$-values are concerning. This is because the $p$-values are not very smooth on the surfaces of the sample. It should be expected that small $p$-values are in areas of the defects. Pixels are tested positive, or considered to be evidence of a defect, when $\|z_{x,y}\|>\inputNumber{../figures/inference/inferenceIntro_critical.txt}$. This value was chosen by controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} (BH) procedure. The positive pixels are shown in Figure \ref{fig:inference_inferenceIntro_inference_positivePixels}.

@@

Model misspecification appeared to be the main source of error. The $z$ statistics and $p$-values were inspected in Figure \ref{fig:inference_inferenceIntro_histogram}. It can be seen that the majority of the $z$ statistics does not look Normal. Also the majority of the $p$-values does not look uniformly distributed. This seems to suggest that the assumption of $Z_{x,y}\sim \normal(0,1)$ is incorrect.

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_histogram.eps}
    \caption{Histogram of $z$}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_pValue.eps}
    \caption{$p$-values}
  \end{subfigure}
}
  \caption{a) The histogram of the $z$ statistics is compared with the standard Normal distribution. The standard Normal distribution is known as the null distribution in this scenario. b) The $p$-values are ordered and plotted. The critical region corresponds to controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} procedure.}
  \label{fig:inference_inferenceIntro_histogram}
\end{figure}

This chapter recaps hypothesis testing, for a single test and then for multiple tests, treating each pixel as a test. Assumptions used on the hypothesis testing can be relaxed using the empirical null \citep{efron2004large}, which is reviewed here. The empirical null is then extended to an image filter, called the empirical null filter. This filter adjust each $z$ statistic according to its neighbours, ironing out false positive results. Simulations and results are shown towards the end of the chapter.

@@

The Newton-Raphson method is an iterative algorithm and requires an initial value $z^{(0)}$. The iterative step is
\begin{equation}
  z^{(r+1)} =
  z^{(r)}
  -\dfrac{
    \left.
      \dfrac{
        \partial
      }
      {
        \partial z
      }
      \ln\widehat{p}_Z(z)
    \right|_{z = z^{(r)}}
  }
  {
    \left.
      \dfrac{
        \partial^2
      }
      {
        \partial z^2
      }
      \ln\widehat{p}_Z(z)
    \right|_{z = z^{(r)}}
  } 
\end{equation}
for $r=0,1,2,3,\dotdotdot$ until some convergence condition is met. The derivatives for the log density was obtained via the following. Recall that the kernel density estimate is
\begin{equation}
  \widehat{p}_Z(z)=
  \frac{1}{nh}
  \sum_{i=1}^n\phi\left(
    \dfrac{z_i-z}{h}
  \right)
  \tag{\ref{eq:inference_kernel_density_estimate}}
\end{equation}
so that the log density is
\begin{equation}
  \ln\widehat{p}_Z(z)=
  \ln\left(
    \dfrac{1}{nh}
  \right)
  +
  \ln\left[
    \sum_{i=1}^n
    \phi\left(
      \dfrac{
        z_i - z
      }
      {
        h
      }
    \right)
  \right]
  \ .
\end{equation}
Taking the first derivative
\begin{equation}
  \dfrac{
    \partial
  }
  {
    \partial z
  }
  \ln\widehat{p}_Z(z)
  =
  \dfrac{
    1
  }
  {
    \sum_{i=1}^n
    \phi\left(
      \dfrac{
        z_i - z
      }
      {
        h
      }
    \right)
  }
  \times
  \sum_{i=1}^n
  \phi'\left(
    \dfrac{
      z_i - z
    }
    {
      h
    }
  \right)
  \left(
    -\dfrac{
      1
    }
    {
      h
    }
  \right)
  \ .
\end{equation}
Using the fact that $\phi(z)=(2\pi)^{-1/2}\exp(-z^2/2)$, then $\phi'(z)=-z\phi(z)$. This is used to simplify the equation to be
\begin{equation}
  \dfrac{
    \partial
  }
  {
    \partial z
  }
  \ln\widehat{p}_Z(z)
  =
  \dfrac{
    \sum_{i=1}^n
    \phi\left(
      \dfrac{
        z_i - z
      }
      {
        h
      }
    \right)
    \left(
      \dfrac{
        z_i - z
      }
      {
        h
      }
    \right)
  }
  {
    h
    \sum_{i=1}^n
    \phi\left(
      \dfrac{
        z_i - z
      }
      {
        h
      }
    \right)
  }
  \ .
\end{equation}
Taking the derivative again
\begin{multline}
  \dfrac{
    \partial^2
  }
  {
    \partial z^2
  }
  \ln\widehat{p}_Z(z)
  =
  \left[
    h\sum_{i=1}^n
    \phi\left(
      \dfrac{
        z_i-z
      }
      {
        h
      }
    \right)
  \right]^{-2}
  \times
  \left\{
    h\left[
      \sum_{i=1}^n
      \phi\left(
        \dfrac{
          z_i-z
        }
        {
          h
        }
      \right)
    \right]
  \right.
  \\
  \left.
    \times
    \sum_{i=1}^n\left[
      \phi'\left(
        \dfrac{
          z_i-z
        }
        {
          h
        }
      \right)
      \left(
        -\dfrac{
          1
        }
        {
          h
        }
      \right)
      \left(
        \dfrac{
          z_i-z
        }
        {
          h
        }
      \right)
      +\phi\left(
        \dfrac{
          z_i-z
        }
        {
          h
        }
      \right)
      \left(
        -\dfrac{
          1
        }
        {
          h
        }
      \right)
    \right]
  \right.
  \\
  \left.
    -
    \left[
      \sum_{i=1}^n
      \phi\left(
        \dfrac{
          z_i-z
        }
        {
          h
        }
      \right)
      \left(
        \dfrac{
          z_i-z
        }
        {
          h
        }
      \right)
    \right]
    \left[
      h\sum_{i=1}^n
      \phi'\left(
        \dfrac{
          z_i-z
        }
        {
          h
        }
      \right)
      \left(
        -\dfrac{
          1
        }
        {
          h
        }
      \right)
    \right]
  \right\}
  \ .
\end{multline}
Using the fact that $\phi'(z)=-z\phi(z)$, then it is simplified to
\begin{multline}
  \dfrac{
    \partial^2
  }
  {
    \partial z^2
  }
  \ln\widehat{p}_Z(z)
  =
  \left[
    h\sum_{i=1}^n
    \phi\left(
      \dfrac{
        z_i-z
      }
      {
        h
      }
    \right)
  \right]^{-2}
  \times
  \left\{
    \left[
      \sum_{i=1}^n
      \phi\left(
        \dfrac{
          z_i-z
        }
        {
          h
        }
      \right)
    \right]
  \right.
  \\
  \left.
    \times
    \left[
      \sum_{i=1}^n
      \phi\left(
        \dfrac{
          z_i-z
        }
        {
          h
        }
      \right)
      \left(
        \left(
          \dfrac{
            z_i-z
          }
          {
            h
          }
        \right)^2
        -1
      \right)
    \right]
    -
    \left[
      \sum_{i=1}^n
      \phi\left(
        \dfrac{
          z_i-z
        }
        {
          h
        }
      \right)
    \right.
  \right.
  \\
  \left.
    \left.
      \left(
        \dfrac{
          z_i-z
        }
        {
          h
        }
      \right)
    \right]^2
  \right\}
  \ .
\end{multline}

@@

\subsection{Approximate Properties of $\widehat{\sigma}_0$}

@@

The choice of the bandwidth $h$ is important for the kernel density estimator. It controls how smooth the kernel density estimator is, with higher values of $h$ producing smoother curves \citep{friedman2001elements}. Cross validation methods do exist \citep{bowman1984alternative, sheather2004density} but they can be computationally expensive. Rules of thumb \citep{silverman1986density, sheather2004density} can be used instead and are typically of the form
\begin{equation}
  h = bn^{-1/5}\times\text{min}\left(s_z,\text{IQR}_z/1.34\right)
\end{equation}
where $b=0.9$ \citep{silverman1986density}. This rule of thumb was developed with consideration of bimodal Normal distributions \citep{silverman1986density}. Other options include $b=1.06$ and $b=1.144$ to produce smoother curves \citep{silverman1986density, sheather2004density}.

The kernel density estimator is only used to obtain values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$. Thus a good bandwidth, in the context of the empirical null, is one which has good properties of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ rather than the density estimate. However exact properties of these estimators based on the kernel density estimators can be rather complicated. Empirical properties were studied here.

An experiment was conducted to investigate the behaviour of the estimators, $\widehat{\mu}_0$ and $\widehat{\sigma}_0$, on a dataset of $n$ simulated all null $\normal(0,1)$. Various values of $h$ and $n$ were investigated. For a given $h$ and $n$, 100 values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ were obtained by repeating the simulation. The median squared error was obtained by taking the median over all squared errors from the 100 estimates. Figure \ref{fig:inference_BandwidthSelection_error} shows the resulting median squared errors.

@@

A smooth valley can be seen for the median squared error for $\widehat{\sigma}_0$. It appears for a given $n$, there exist a bandwidth which minimise the median squared error. However the rules of thumb does not optimise for $\widehat{\sigma}_0$ and undershoots it. Figure \ref{fig:inference_BandwidthSelection_error3} shows the median of the estimates of $\sigma_0$. The true value in this simulation is $\sigma_0=1$ which is represented as a horizontal plane. Bandwidths too small underestimate $\sigma_0$, bandwidths too big over estimates $\sigma_0$.

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error1.eps}
      \caption{$\mu_0$}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error2.eps}
      \caption{$\sigma_0$}
  \end{subfigure}
  \caption{Median squared error of the estimators of the empirical null parameters from 100 repeats of $n$ simulated $\normal(0,1)$ data. Lines represent the rule of thumb for various values of $b$.}
  \label{fig:inference_BandwidthSelection_error}
\end{figure}

\begin{figure}
  \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error3.eps}
        \caption{Heatmap}
    \end{subfigure}
    \caption{Median value of $\widehat{\sigma}_0$ from 100 repeats of $n$ simulated $\normal(0,1)$ data. The true value is $\sigma_0=1$ which is represented by a horizontal plane.}
    \label{fig:inference_BandwidthSelection_error3}
\end{figure}

Overestimates and underestimates are both dangerous and it can affect the false positive and false negative rate. This is because $\widehat{\sigma}_0$ was used to rescale the test statistics accordingly. Recall that the corrected test statistics are
\begin{equation}
  t_i = \dfrac{
    z_i - \widehat{\mu}_0
  }
  {
    \widehat{\sigma}_0
  }
  \ .
  \tag{\ref{eq:inference_zeta}}
\end{equation}
Low values of $\widehat{\sigma}_0$ produce large values in magnitude of $t_i$, potentially testing more of these test statistics as positive. High values of $\widehat{\sigma}_0$ does the opposite. Large number of positives can led to more false positives and vice versa.

The optimal bandwidth for a given $n$ was found numerically. Figure \ref{fig:inference_BandwidthSelection2_plot} shows the log squared error against the bandwidth for various $n$. A smoothing spline \citep{friedman2001elements} was fitted and this was optimised to find the bandwidth which minimises the log squared error for a given $n$.

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot1.eps}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot51.eps}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot100.eps}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot150.eps}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot199.eps}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot249.eps}
    \end{subfigure}
    }
    \caption{A smoothing spline was fitted on the log squared error for estimating $\sigma_0$ against the bandwidth. The estimator $\widehat{\sigma}_0$ uses the kernel density estimator fitted onto $n$ simulated standard Normal data. Boxplots represent the variation of the error from 100 repeats. The red dashed line shows the bandwidth which minimise the fitted spline.}
    \label{fig:inference_BandwidthSelection2_plot}
\end{figure}

A relationship between the optimal bandwidth and $n$ was attempted to be found. It was assumed such a relationship has the linear from
\begin{equation}
  h_{\text{optimal}} = b n^{-1/5} + a
\end{equation}
where $b$ and $a$ are parameters to be fitted. Figure \ref{fig:inference_BandwidthSelection2_ruleOfThumb} show the fitting of an identity link gamma GLM in order to estimate $b$ and $a$. The estimated parameters are shown in Table \ref{table:inference_BandwidthSelection2_ruleOfThumb}.
